\begin{thebibliography}{9}
\bibitem{3gpp36321}
3GPP TS 36.321 Medium Access Control (MAC) protocol specification, Release 15, 2020
\bibitem{3gpp38321}
3GPP TS 38.321 Medium Access Control (MAC) protocol specification, Release 15, 2020
\bibitem{3gpp25319}
3GPP TS 25.319 Enhanced uplink; Overall description, Release 13, 2016
\bibitem{ETSITS136213}
Evolved Universal Terrestrial Radio Access (E-UTRA), Physical layer procedures 
\bibitem{multiple_access_protocols}
Multiple Access Protocols, Performance and Analyisis, Raphael Rom, Moshe Sidi 
\bibitem{shannon_theory}
A Mathematical Theory of Communication, By C. E. SHANNON
\bibitem{information_centric}
Din, I.U., Asmat, H. and Guizani, M. A review of information centric network-based internet of things: communication architectures, design issues, and research opportunities. Multimed Tools Appl 78, 30241–30256 (2019). 
\bibitem{lte_advaned_mobile}
4G: LTE/LTE-Advanced for Mobile Broadband, Erik Dahlman, Stefan Parkvall, Johan Skold
\bibitem{tbma}
G. Mergen and L. Tong, "Type based Estimation over Multiaccess Channels" in IEEE 
\bibitem{access_tech}
Chen, W.K., "The Electrical Engineering Handbook", P.1005, Section 7.1 Access Technologies, 2004.
\bibitem{mod_impact}
Impact of Modulation Schemes on LTE, Juhi Pruthi, Pooja Agarwal, Nikita Jain.
\bibitem{umts_sesia}
LTE – The UMTS Long Term Evolution: From Theory to Practice Stefania Sesia, Issam Toufik and Matthew Baker.
\bibitem{csi_defs}
R\&STS8980 test system analyzes LTE quality indicators: CQI, PMI and RI
WIRELESS TECHNOLOGIES | Conformance test systems. 
\bibitem{fdma_info}
Chen, W.K., "The Electrical Engineering Handbook", P.1005, Section 7.1.1 FDMA, 2004. 
\bibitem{tdma_info}
Chen, W.K., "The Electrical Engineering Handbook", P.1006, Section 7.1.2 TDMA, 2004.
\bibitem{cdma_info}
Chen, W.K., "The Electrical Engineering Handbook", P.1007, Section 7.1.3 CDMA, 2004.
\bibitem{ofdma_info}
Sassan Ahmadi, LTE-Advanced,2014. Orthogonal Frequency Division Multiple Access. Section 9.5
\bibitem{srsLTE}
srsLTE opensource project, https://www.srslte.com/ 
\bibitem{los_pic}
Line of Sight Infographic, https://unlimitedlteadvanced.com/4g-lte/how-do-i-choose-a-4g-lte-antenna/
\bibitem{interference_pic}
http://hydrogen.physik.uni-wuppertal.de/hyperphysics/hyperphysics/hbase/sound/interf.html
\end{thebibliography}